A multi-dimensional extension of the Lightweight Temporary Compression method

### 2018-10-05 paper.tex
Started describing original LTC algorithm

@@

Summarize existing paper.

Lightweight temporal compression (LTC) is one of the linear estimation 
method to compress data. It is The first-order interpolator with two 
degrees of freedom(FOI-2DF) which is mentioned in 
~\cite{jalaleddine1990ecg}.  Most of linear estimation method need a 
predefined parameter which is the error margin (let's call $\epsilon$) 
in order to guarantee the difference between estimation and original 
data within a scope.

\todo{rewrite LTC algorithm, and there is a DP version of LTC maybe should also be written}

>>>>

% Some related works from Bo's report

% transmitted, received points

% contributions: formalization of LTC algorithm, extension to n d, extension to any norm, open-source implementation.

@@

Lightweight Temporal Compression 
(LTC~\cite{schoellhammer2004lightweight}) approximates the data stream 
by a piece-wise linear function of time, ensuring that the error at 
every time-point is bounded.

\subsection{Notations}

We use the following notations and assumptions to describe the LTC algorithm.
The algorithm \emph{receives} a stream of \emph{data points} $x_i$
at times $t_i$ ($i \in \mathbb{N}$), and it \emph{transmits} a stream of data points $\xi_i$ 
at times $\tau_i$ ($i \in \mathbb{N}$). To simplify the notations, we assume that:
\begin{equation*}
\forall k \in \mathbb{N}, \  \exists ! j \in \mathbb{N} \  \xi_k = t_j
\end{equation*}
That is, transmission times coincide with reception times. 
We define the \emph{centered received points} as follows:
\begin{equation*}
\forall k \in \mathbb{N}\ , \forall i \in \mathbb{N},\ (u^k_i, y^k_i) = (t_{j+i} - t_j, x_{j+i}), \quad \mathrm{where}\ t_j = \xi_k.
\end{equation*}
This definition is such that $u^k_0=0$, and $y^k_i$ is the $i^{th}$ point received
after the $k^{th}$ transmission.

\subsection{LTC algorithm}

Using the notations defined previously, the original LTC algorithm is written as 
follows:
% define x_i (1D), (t, x_i)
\begin{enumerate}
\item Initialization, after $k^{th}$ transmission:
    \begin{itemize}
        \item Wait until first point $(u^k_1, y^k_1)$ is received.
        \item UL $\leftarrow$ $(u^k_1, y^k_1+\epsilon)$
        \item LL $\leftarrow$ $(u^k_1, y^k_1-\epsilon)$
    \end{itemize}
\item Calculate \emph{highLine} as the line connecting $(u^k_0, y^k_0)$ and UL.
\item Calculate \emph{lowLine} as the line connecting $(u^k_0, y^k_0)$ and LL.
\end{enumerate}

 %~ is one of the linear estimation 
%~ method to compress data. It is The first-order interpolator with two 
%~ degrees of freedom (FOI-2DF) which is mentioned in 
%~ ~\cite{jalaleddine1990ecg}.  Most of linear estimation method need a 
%~ predefined parameter which is the error margin (let's call $\epsilon$) 
%~ in order to guarantee the difference between estimation and original 
%~ data within a scope.

%~ \todo{rewrite LTC algorithm, and there is a DP version of LTC maybe should also be written}
